\section{Research and Engineering Experience}
% Design Team 5
\cventry
{1/20 -- 5/21}
{Design Team Leader}
{\href{https://cbid.bme.jhu.edu/academics/undergraduate-studies/}{Dept. of Biomedical Engineering}}
{Johns Hopkins University}
{}
{
\begin{itemize}
    \item Team leader and project manager for a team of eight undergraduate engineers.
    % \item Improving the accuracy of device deployment during minimally invasive percutaneous heart surgery.
    \item Developed a multi-modal spatiotemporal registration algorithm to power a dynamic fusion image guidance system for minimally invasive heart surgery.
    \item \textbf{Skills used:} \textit{Computer vision, image registration, cardiology, Python, and Git.}
\end{itemize}{}
}

% Neurodata
\cventry
{9/18 -- 5/21}
{Undergraduate Research Assistant}
{\href{https://neurodata.io}{Neurodata Lab}}
{Johns Hopkins University}
{}
{
\begin{itemize}
    % \item Developing Random Forest-based computer vision algorithm for brain tumor segmentation.
    % \item Developed novel split criteria to enable accurate high-dimensional regression using the Random Forest algorithm.
    \item Developed novel machine learning methods for analyzing populations of graph-valued objects \cite{gopalakrishnanMultiscaleComparativeConnectomics2020, chungStatisticalConnectomics2020b}.
    \item Discovered neuro-connectively similar subtypes of autism using joint embeddings of multi-network connectomes \cite{wangVariabilityHeritabilityMouse2020, gopalakrishnanBMES2019}.
    \item \textbf{Skills used:} \textit{Graph theory, statistics, machine learning, Python, and Git.}
\end{itemize}
}

% Ragon
\cventry
{Summer 2018}
{Summer Student Researcher}
{\href{http://www.ragoninstitute.org/portfolio-item/ghebremichael/}{Ghebremichael Lab}}
{Ragon Institute of MGH, MIT and Harvard}
{}
{
\begin{itemize}
    \item Developed predictive models of disease progression and immune recovery in HIV-positive children with TB co-infection \cite{gopalakrishnanPreHAARTCD4Tlymphocytes2020}.
    \item Identified biomarkers for antiretroviral toxicity by applying machine learning methods to HIV-patient data \cite{leeComparisonMachineLearning2019a}.
    \item \textbf{Skills used:} \textit{Survival analysis, ROC models, R, and Git.}
\end{itemize}{}
}

% Design Team 12
\cventry
{12/17 -- 5/18}
{Design Team Member}
{\href{https://cbid.bme.jhu.edu/academics/undergraduate-studies/}{Dept. of Biomedical Engineering}}
{Johns Hopkins University}
{}
{
\begin{itemize}
    \item Designed and implemented a clinical machine learning algorithm to predict the onset of lung failure in pediatric patients.
    \item \textbf{Skills used:} \textit{Representation learning, sparse dictionary learning, Python, and Git.}
\end{itemize}{}
}

% FBK
\cventry
{6/17 -- 7/17}
{Summer Researcher}
{\href{https://webvalley.fbk.eu}{Fondazione Bruno Kessler}}
{Trento, Italy}
{}
{
\begin{itemize}
    \item Implemented a deep learning algorithm to quantitatively assess crop damage from images taken by farmers.
    \item \textbf{Skills used:} \textit{Computer vision, Keras, Python, and Git.}
\end{itemize}{}
}

% Walt Lab
\cventry
{6/16 -- 6/17}
{High School Researcher}
{\href{http://ase.tufts.edu/chemistry/walt/sepa/index.html}{Tufts University BioSeq Program}}
{Tufts University}
{}
{
\begin{itemize}
    \item Used next-generation sequencing (NGS) to generate a novel human oral microbiome data set.
    \item Analyzed sequence data using dimensionality reduction and hidden Markov models to identify microbial biomarkers of oral health.
    \item Presented at the 2017 Intel International Science and Engineering Fair, Los Angeles, CA.
    \item \textbf{Skills used:} \textit{DNA library construction, next-generation sequencing, dimensionality reduction, hidden Markov models, and R.}
\end{itemize}{}
}